---
title: "Grouped Pine"
author: "The Nature Conservancy"
date: "12/13/2021"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Grouped pine data and charts
Pine data was grouped as follows:

* B-C-D (2.6 - 15 cm)
* E-F-G (15.1 - 30 cm)
* H-I-J (30.1-40+ cm)
* Pre-breast height (0 - 2.5cm)


Note, colors are different from other charts to hopefully prevent confusion.

**Seedlings not included in data**

```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR, viridis)
theme_set(theme_bw(base_size = 16))

# get data and remove seedlings
groupedPine <- read_csv("data/pineAll.csv")%>%
      filter(`SIZE(noCM)` != "SEEDLING")
                
```

### Data Table
The cleaned Pine data for class A is served up below.  

<br>

```{r pineDT, echo=FALSE, message=FALSE, warning=FALSE}

datatable(groupedPine,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'))))
```

<br>



## Summary Chart-line of groups over time


```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

meanGroupedPine <- groupedPine %>%
  group_by(PRES,  GROUPS,  MONYEAR)%>%
  summarise(meanSTEMS = mean(STEMS))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=10, fig.height=7}
stemsSizeYear <-meanGroupedPine %>%

 ggplot(aes(x= MONYEAR, y= meanSTEMS, group = GROUPS, color = GROUPS)) +
  geom_line(size=1.5) +
  geom_point(size =  2.0) +
  # My top color palette
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE)  +
  # Update the labels of the axes
  labs(x = "Year",
       y = "Mean number of stems per year at ABRP",
       title = "",
       caption = "Data from Florida Chapter",
       color = "Grouped Stem Size (in CM)")  +

  #Adjust the axes
  theme(plot.title = element_text(face="bold"),
        axis.title.x = element_text(face="bold"),
        axis.title.y = element_text(face="bold"),
        legend.title = element_text(face="bold")) 

stemsSizeYear


```


<br>

## Grouped pine stems per Burn Unit-Plot

 To view a plot select from dropdown, or download compiled PDF [here](https://github.com/rswaty/ABRPweb/raw/master/groupedPineStems.pdf). 



```{r sum grouped pine, message=FALSE, warning=FALSE, include=FALSE}
sumsGroupedPine <- groupedPine %>%
  group_by(PRES,  GROUPS,  MONYEAR, BP)%>%
  summarise(sumSTEMS = sum(STEMS))
```


```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdSumsGroupedPine <- highlight_key(sumsGroupedPine)

```


```{r selectable pine groups, echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=11}
groupedPinePlotStems <-  
ggplot(sdSumsGroupedPine, aes(MONYEAR, sumSTEMS, color = GROUPS, group = GROUPS)) +
  geom_line(size=1.5, position = position_jitter(width = 0.0001, height = 1.0)) +
  geom_point() +
  theme_bw() +
  labs(
    title = "",
    caption = "Data from TNC's Florida Chapter",
    x = "Monitoring Year",
    y = "Number of stems",
    color = "Grouped Stem Size (in CM)") + 
  scale_color_viridis(discrete = TRUE, option = "D")


bscols(widths = c(5, 12),
       filter_select("BP", 
                     "Plot:", 
                     sdSumsGroupedPine, 
                     ~ BP,
                     multiple = FALSE),
       ggplotly(groupedPinePlotStems)
)
```

