---
title: "Grouped Pine Data"
author: "The Nature Conservancy's LANDFIRE team"
date: "12/13/2021"
output: html_document
---



```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR, viridis)


groupedPine <- read_csv("data/groupedPine.csv")
```

# This page...
Has charts of pine data grouped into 4 categories (on charts, measurements in CM) as a way of summarizing and easing interpretation.  Note, colors are different from other charts to hopefully prevent confusion.



## Summary Chart-line of groups over time


```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

summaryGroupedPine <- groupedPine %>%
  group_by(PRES,  GROUPS,  MONYEAR)%>%
  summarise(meanSTEMS = mean(STEMS))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=11}
stemsSizeYear <-summaryGroupedPine %>%

 ggplot(aes(x= MONYEAR, y= meanSTEMS, group = GROUPS, color = GROUPS)) +
  geom_line(size=1.5) +
  geom_point(size =  2.0) +

  # My top color palette
  
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE)  +

  # Theme
  theme_bw() +


  # Update the labels of the axes
  labs(x = "Year",
       y = "Mean number of stems per year at ABRP",
       title = "",
       caption = "Data from Florida Chapter",
       color = "Grouped Stem Size (in CM)")  +

  #Adjust the axes
  theme(plot.title = element_text(face="bold", size =20),
        axis.title.x = element_text(face="bold", size = 20),
        axis.title.y = element_text(face="bold", size = 20),
        legend.title = element_text(face="bold", size = 20)) 

stemsSizeYear


```


<br>

## Selectable Grouped Pine Chart

## Number of stems per size class category.  To view limited number of plots select from dropdown, or download compiled PDF [here](https://github.com/rswaty/ABRPweb/raw/master/groupedPineStemCharts.pdf). 

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdGroupedPine <- highlight_key(groupedPine)

```


```{r selectable pine groups, echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=11}
groupedPinePlotStems <-  
ggplot(sdGroupedPine, aes(MONYEAR, STEMS, color = GROUPS, group = GROUPS)) +
  geom_line(size=1.5, position = position_jitter(width = 0.0001, height = 1.0)) +

  geom_point() +
  theme_bw() +
  labs(
    title = "",
    caption = "Data from TNC's Florida Chapter",
    x = "Monitoring Year",
    y = "Number of stems",
       color = "Grouped Stem Size (in CM)") + 
  scale_color_viridis(discrete = TRUE, option = "D")+
  scale_fill_viridis(discrete = TRUE) 

bscols(widths = c(5, 12),
       filter_select("BP", "Plot:", sdGroupedPine, ~ BP),
       ggplotly(groupedPinePlotStems)
)
```

