---
title: "Herbaceous data"
author: "rswaty"
date: "2021-08-02"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Herbaceous Data

### Data cleaning notes

* All cleaned Herbaceous data saved as "herbWU.csv"
* For Perennial Grasses, that data was copied and pasted into a new spreadsheet, "perGrass.csv".   Used Pivot Table to create this new spreadsheet.  
* Assumed "99999" meant "no data". Changed to "NA".  Looks like (at least for some years) only one quadrat was sampled for % PG, % WP, % OP, % LI AND % BG.
* Did nothing with blank cells.
* Deleted rows with AVERAGES
* * Bull-dozing happened (instead of fire?) for MONYEAR 2007, B-Ps 7_8, 7_7, 7_6, and 7_4.  Did not transfer this information to LASTBURNYEAR (but is is in LASTBURN column). Swaty did not want to mix numerical and text data types in the LASTBURNYEAR column.
* In perGrass.csv:
    * deleted 21_4 data for 2001
    * deleted 40_10 data for 1998
    * recalculated average and standard dev for 2010, BP 7_1
    * fixed missing years for BP 7_1
    * recalculated average and st. deviation for 40_2 (there were multiples)


```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce)
theme_set(theme_bw())
```

```{r readPerGRass, message=FALSE, warning=FALSE, include=FALSE}
perGrass <- read_csv("data/perGrass.csv")

```

### Perennial Grass Data Table
The cleaned Perennial data is served up below.  

<br>

```{r perGrassDT, echo=FALSE, message=FALSE, warning=FALSE}


datatable(perGrass,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'))))
```

<br>


### All Herbaceious Data Table
The cleaned Perennial data is served up below.  

<br>

```{r herbDT, echo=FALSE, message=FALSE, warning=FALSE}

herbWU <- read_csv("data/herbWU.csv")

datatable(herbWU,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'))))
```

<br>




### Number of observations variable over time

```{r PGobs, echo=FALSE, message=FALSE, warning=FALSE}

yearObsPG <-
perGrass %>%
  count(MONYEAR)

yearObsPGChart <-
  yearObsPG %>%
  ggplot(aes(x = MONYEAR, y = n)) +
  geom_line(size = 1.5) +
  labs(x = "Year",
       y = "Number of rows",
       title = "Number of observations per year",
       caption = "Data from Florida Chapter")  +


  #Adjust the axes
  theme(plot.title = element_text(face="bold", size =14),
        axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12),
        legend.title = element_text(face="bold", size = 12))


yearObsPGChart
```

