---
title: "Perinnieal grass charts"
author: "The Nature Conservancy's LANDFIRE team"
date: "7/13/2021"
output: html_document
---


## Herbaceous Data 16 November 2021

### Data cleaning notes

* Saved as "herbWU.xsls"
* Assumed "99999" meant "no data". Changed to "NA".  Looks like (at least for some years) only one quadrat was sampled for % PG, % WP, % OP, % LI AND % BG.
* Did nothing with blank cells.
* Deleted row with AVERAGES
* * Bull-dozing happened (instead of fire?) for MONYEAR 2007, B-Ps 7_8, 7_7, 7_6, and 7_4.  Did not transfer this information to LASTBURNYEAR (but is is in LASTBURN column). Swaty did not want to mix numerical and text data types in the LASTBURNYEAR column.


```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce)
theme_set(theme_bw())
```

```{r perGrassData, message=FALSE, warning=FALSE, include=FALSE}
perGrass <- read_csv("data/perGrass.csv")

```


# Jittered boxplots of percent perinnial grass over time

```{r perGrassBox, echo=FALSE, message=FALSE, warning=FALSE}
explorePerGrass <-
  perGrass %>%
  ggplot(aes(x = MONYEAR, y = meanPerPG, group = MONYEAR)) +
  geom_boxplot(position = position_dodge(width = 0.9),
               fill = "#4287f5",
               alpha = 0.5) +
  geom_jitter(width = 0.25) +
  theme_bw() +
  labs(x = "Year",
       y = "Cover",
       title = "Wiregrass cover per plot",
       subtitle = "Dots jittered so that they would not totally overlap",
       caption = "Data from Florida Chapter")  +

  #Adjust the axes, remove legend
  theme(legend.position = "none",
        plot.title = element_text(face="bold", size =14),
        axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))



explorePerGrass
```






## Percent perinneal grass over time per BU_P.  To view limited number of BU-Ps select from dropdown, or download compiled PDF [here](https://github.com/rswaty/ABRPweb/raw/master/wiregrassCharts.pdf).  

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdPerGrass <- highlight_key(perGrass)

```



```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
perGrassPlot <-  
ggplot(sdPerGrass, aes(MONYEAR, meanPerPG, group = BP)) +
  geom_line(size=1.5, position = position_jitter(width = 0.0001, height = 1.0)) +
  geom_point() +
  theme_bw() +
  labs(
    title = "Average Percent Perinnial Grass per plot",
    subtitle = "Ignore BU-plot 21_4.  It appears to be a data issue, but we decided to not delete the data.",
    caption = "Data from TNC's Florida Chapter",
    x = "Monitoring Year",
    y = "Mean Percent" ) +
  scale_color_simpsons()

bscols(widths = c(5, 12),
       filter_select("BP", "Plot:", sdPerGrass, ~ BP),
       ggplotly(perGrassPlot)
)

```
