---
title: "Perinnieal grass"
author: "The Nature Conservancy's LANDFIRE team"
date: "7/13/2021"
output: html_document
---


## Herbaceous Data

### Data cleaning notes

* Saved as "herbWU.xsls"
* Assumed "99999" meant "no data". Changed to "NA".  Looks like (at least for some years) only one quadrat was sampled for % PG, % WP, % OP, % LI AND % BG.
* Did nothing with blank cells.
* Deleted row with AVERAGES
* * Bull-dozing happened (instead of fire?) for MONYEAR 2007, B-Ps 7_8, 7_7, 7_6, and 7_4.  Did not transfer this information to LASTBURNYEAR (but is is in LASTBURN column). Swaty did not want to mix numerical and text data types in the LASTBURNYEAR column.


```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR)
theme_set(theme_bw())
```

```{r}
perGrass <- read_csv("data/perGrass.csv")
View(perGrass)
```




## Number of stems per size class category.  To view limited number of plots select from dropdown. 

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdPerGrass <- highlight_key(perGrass)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
perGrassPlot <-  
ggplot(sdPerGrass, aes(MONYEAR, meanPerPG, group = BP)) +
  geom_line(size=1.5, position = position_jitter(width = 0.0001, height = 1.0)) +
  geom_point() +
  theme_bw() +
  labs(
    title = "Average Percent Perinnial Grass per plot",
    subtitle = "",
    caption = "Data from TNC's Florida Chapter",
    x = "Monitoring Year",
    y = "Mean Percent" ) +
  scale_color_simpsons()

bscols(widths = c(5, 12),
       filter_select("BP", "Plot:", sdPerGrass, ~ BP),
       ggplotly(perGrassPlot)
)

```
