---
title: "Pine Charts"
author: "rswaty"
date: "2021-07-06"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR)
theme_set(theme_bw())
```

## This page...
On this page several ways to explore patterns in Pine stems are presented.  Some are interactive; all will take a bit of time to digest and interpret.  There are over 5,280 observations from 57 plots that occurred from 1995-2020.


## Number of pine stems per plot variable with high of 512 (BP 7_8, 2017)

<br>

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

pine <- read_csv("data/pine.csv")
pine %>%
  mutate(MONYEAR = as.character(MONYEAR))
```


```{r numStems, echo=FALSE, message=FALSE, warning=FALSE}

stemsExplore <-
  pine %>%
  ggplot(aes(x = MONYEAR, y = STEMS, group = MONYEAR, fill = MONYEAR)) +
  geom_boxplot(position = position_dodge(width = 0.9)) +
  geom_point(position = position_jitterdodge(seed = 1, dodge.width = 0.9)) +
  theme_bw() +
  labs(x = "Year",
       y = "Number of stems",
       title = "Total number of stems per plot",
       subtitle = "Dots jittered so that they would not totally overlap",
       caption = "Data from Florida Chapter")  +

  #Adjust the axes, remove legend
  theme(legend.position = "none",
        plot.title = element_text(face="bold", size =14),
        axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12))



stemsExplore


```

## Stem size per year

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

groupedPine <- pine %>%
  group_by(PRES,  SIZE,  MONYEAR)%>%
  summarise(meanSTEMS = mean(STEMS))
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
stemsSizeYear <-groupedPine %>%

 ggplot(aes(x= MONYEAR, y= meanSTEMS, group = SIZE, color = SIZE)) +
  geom_line(size=1.5) +
  geom_point(size =  2.0) +

  # My top color palette
  scale_color_simpsons() +

  # Theme
  theme_bw() +


  # Update the labels of the axes
  labs(x = "Year",
       y = "Mean number of stems per year at ABRP",
       title = "Summarizing number of stems across size categories",
       caption = "Data from Florida Chapter",
       color = "Stem Size")  +

  #Adjust the axes
  theme(plot.title = element_text(face="bold", size =14),
        axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12),
        legend.title = element_text(face="bold", size = 12))
stemsSizeYear
```



## Number of stems per size class category.  To view limited number of plots select from dropdown. 

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdPine <- highlight_key(pine)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
pinePlotStems <-  
ggplot(sdPine, aes(MONYEAR, STEMS, color = SIZE, group = BP)) +
  geom_line(size=1.5, position = position_jitter(width = 0.0001, height = 1.0)) +

  geom_point() +
  theme_bw() +
  labs(
    title = "Pine stems per plot",
    subtitle = "Including size class",
    caption = "Data from TNC's Florida Chapter",
    x = "Monitoring Year",
    y = "Number of stems" ) +
  scale_color_simpsons()

bscols(widths = c(5, 12),
       filter_select("BP", "Plot:", sdPine, ~ BP),
       ggplotly(pinePlotStems)
)

```

## Stems compared to plots in BU 5

```{r vsBU5data, message=FALSE, warning=FALSE, include=FALSE}

# read data
averagePineStemsBU <- read_csv("data/averagePineStemsBU.csv") #renamed AVERAGE_STEMS to STEMS


pineBU5all <- read_csv("data/pineBU5all.csv")
```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=30, fig.width = 10 }
stemsSizeYearBU <-

  ggplot(data = averagePineStemsBU, aes(x= MONYEAR, y= STEMS, group = BU, color = as.factor(BU))) +
  geom_line(size=0.5) +
  geom_point(size =  1.5) +
  geom_smooth(data = pineBU5all, method=lm, size = 1.0, color = "black" ) +
  facet_wrap(~ SIZE, ncol = 1, scales = "free_y") +


  # My top color palette
  scale_color_simpsons() +



  # Update the labels of the axes
  labs(x = "Year",
       y = "Mean number of stems",
       title = "Summarizing number of stems across size categories",
       subtitle = "Black line represented smoothed data and 95% confidence interval from BU 5", 
       caption = "Data from Florida Chapter",
       color = "Burn Unit") 

ggplotly(stemsSizeYearBU)
```



## Heatmap Charts 

These charts compare number of stems per BU_P to the mean number of stems for BU 5.  Notes about the charts:

* Oranges and Reds = fewer stems than mean of stems for BU 5; Greens = more stems than mean of stems for BU 5
* Only shows years where there were counts for BU5 and specific BU_P.
* Ranges are arbitrary, selected by Randy Swaty.  Pay special attention to negatives, and the 0-20 category.  It may be that we need to adjust ranges.
* All the charts are available for download.  Click this [link](https://github.com/rswaty/ABRPweb/raw/master/pineHeatmaps.zip) to download a .zip file.  The file will be automatically downloaded, probably to your "Downloads" folder.
* BPs from Burn Unit 22 and BP 40-10 are missing from charts presumably due to there not being counts for the matching years. 


```{r slickRImages, message=FALSE, warning=FALSE, include=FALSE}

pineImages <- c("heatmapA2.png", 
                "heatmapB2.png",
                "heatmapC2.png",
                "heatmapD2.png",
                "heatmapE2.png",
                "heatmapF2.png",
                "heatmapG2.png",
                "heatmapH2.png",
                "heatmapI2.png",
                "heatmapJ2.png",
                "heatmapSeedlings2.png")

```



```{r slickR, echo=FALSE, message=FALSE, warning=FALSE}

pineSlick <- slickR(obj = pineImages, height=550, width='120%') 
pineSlick

```










