---
title: "pineClassA"
author: "rswaty"
date: "2022-02-09"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR)
theme_set(theme_bw(base_size = 16))
```



## This page...
On this page several ways to explore patterns in class A pine seedlings are presented.  


## Pine class A data table
### Data Table
The cleaned Pine data is served up below.  

<br>

```{r pineDT, echo=FALSE, message=FALSE, warning=FALSE}
classA <- read_csv("data/pineClassAonly.csv")

datatable(classA,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'))))
```

<br>


## Pine class A stems summarized

<br>

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

#install.packages('Rmisc')
library(Rmisc)


classA %>%
  mutate(MONYEAR = as.character(MONYEAR)) 

classAse <- summarySE(classA, measurevar = 'STEMS', groupvars = "MONYEAR")
```


```{r meanSeedlings, echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=10, fig.height=7}



classAexplore <-
  classAse %>%
  ggplot(aes(x = MONYEAR, y = STEMS)) +
  geom_errorbar(aes(ymin=STEMS-se, ymax=STEMS+se), width = 0.2, color = '#9c9991', size = 0.8) +
  geom_line(size = 1.0, color = '#54524d') +
  geom_point() +
  geom_smooth(method=lm) +
  labs(x = "Year",
       y = "Stem count code",
       title = "Mean class A per year",
       subtitle = "Trend line fitted with linear model, level of confidence (SE) = 0.95",
       caption = "Data from Florida Chapter")  +

  #Adjust the axes, remove legend
  theme(legend.position = "none",
        plot.title = element_text(face="bold"),
        axis.title.x = element_text(face="bold"),
        axis.title.y = element_text(face="bold"))

classAexplore 


```


# Class A per BP over time

MAKE PDF AND CHECK LINK
Number of stems per size class category.  To view one plot at a time select from drop down below, or download compiled PDF [here](https://github.com/rswaty/ABRPweb/raw/master/classAstems.pdf). 

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdclassA <- highlight_key(classA)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
pineClassA <-  
ggplot(sdclassA , aes(MONYEAR, STEMS)) +
  geom_line(aes(group = 1), size = 0.5, color = '#54524d') +
  geom_point() +
  labs(
    title = "Pine class A per BU-Plot",
    subtitle = "Including size class",
    caption = "Data from TNC's Florida Chapter",
    x = "Year",
    y = "Stem count code" ) 

bscols(widths = c(5, 12),
       filter_select("BP", 
                     "Plot:", 
                     sdclassA, 
                     ~ BP,
                     multiple = FALSE),
       ggplotly(pineClassA)
)

```

