---
title: "pineData"
author: "rswaty"
date: "2021-07-31"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
## Pine Data


### Data cleaning notes
* worked from data delivered by Beatriz (ABRP_bioplots_1995-2018)[LINK]
* added "B-P" column, concatenated BU and Plot numbers to generate unique value for charts
* added MONYEAR and LASTBURNYEAR columns for charts (also, some burns only had years recorded).  Used "text to columns" tool in Excel with "/" as the delimiter to create new YEAR-based columns where possible.  Manually entered years for many records.
* Bull-dozing happened (instead of fire?) for MONYEAR 2007, B-Ps 7_8, 7_7, 7_6, and 7_4.  Did not transfer this information to LASTBURNYEAR (but is is in LASTBURN column). Swaty did not want to mix numerical and text data types in the LASTBURNYEAR column.
* B-Ps 7_3, 7_5 was missing MONDATE information for 2019.  Swaty manually entered "2019" based on exploring neighboring plots in the dataset.
* Found many typos and case issues (e.g., "Seedling" instead of "SEEDLING")
* In pine.csv:
    * deleted 21_4 data for 2001
    * deleted 40_10 data for 1998


```{r pineDataSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR)
theme_set(theme_bw())
```


### Data Table
The cleaned Pine data is served up below.  

<br>

```{r pineDT, echo=FALSE, message=FALSE, warning=FALSE}
pine <- read_csv("data/pine.csv")

datatable(pine,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'))))
```

<br>

### Number of observations variable over time


```{r obsYear, echo=FALSE, message=FALSE, warning=FALSE}


yearObs <-
pine %>%
  count(MONYEAR)

yearObsChart <-
  yearObs %>%
  ggplot(aes(x = MONYEAR, y = n)) +
  geom_line(size = 1.5) +
  labs(x = "Year",
       y = "Number of rows",
       title = "Number of observations per year",
       caption = "Data from Florida Chapter")  +


  #Adjust the axes
  theme(plot.title = element_text(face="bold", size =14),
        axis.title.x = element_text(face="bold", size = 12),
        axis.title.y = element_text(face="bold", size = 12),
        legend.title = element_text(face="bold", size = 12))


yearObsChart
```
