---
title: "Seedlings"
author: "rswaty"
date: "12/21/2021"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r pineChartsSetup, message=FALSE, warning=FALSE, include=FALSE}
pacman::p_load(tidyverse, ggsci, ggtext, readr, dplyr, DT, crosstalk, plotly, ggforce, slickR)
theme_set(theme_bw(base_size = 16))
```



## This page...
On this page several ways to explore patterns in pine seedlings are presented.  

**Note** 
From 1995-2012 total numbers of pine seedlings were collected in datasheets.  From 2012-2020 numbers of seedlings were coded as follows:

* 1 = 1 - 5 seedlings
* 2 = 6 - 20 seedlings
* 3 = > 21 seedlings

Top charts present coded data, bottom charts present raw data counts, 2012-2020.


## Seedling data table
### Data Table
The cleaned Pine data is served up below.  

<br>

```{r pineDT, echo=FALSE, message=FALSE, warning=FALSE}
seedlings <- read_csv("data/pineSeedlingsOnly.csv")

datatable(seedlings,
  extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = 
      list('copy', 'print', list(
        extend = 'collection',
        buttons = c('csv', 'excel', 'pdf'),
        text = 'Download'))))
```

<br>


## Coded seedlings summarized, 1995-2020

<br>

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

#install.packages('Rmisc')
library(Rmisc)


seedlings %>%
  mutate(MONYEAR = as.character(MONYEAR)) 

seedlingsSE <-  summarySE(seedlings, measurevar = 'STEMS', groupvars = "MONYEAR")
```


```{r meanSeedlings, echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=10, fig.height=7}



seedlingsExplore <-
  seedlingsSE %>%
  ggplot(aes(x = MONYEAR, y = STEMS)) +
  geom_errorbar(aes(ymin=STEMS-se, ymax=STEMS+se), width = 0.2, color = '#9c9991', size = 0.8) +
  geom_line(size = 1.0, color = '#54524d') +
  geom_point() +
  geom_smooth(method=lm) +
  labs(x = "Year",
       y = "Stem count code",
       title = "Mean seedlings (coded) per year",
       subtitle = "Trend line fitted with linear model, level of confidence (SE) = 0.95",
       caption = "Data from Florida Chapter")  +

  #Adjust the axes, remove legend
  theme(legend.position = "none",
        plot.title = element_text(face="bold"),
        axis.title.x = element_text(face="bold"),
        axis.title.y = element_text(face="bold"))

seedlingsExplore


```


# Coded seedlings per BP over time

Number of stems per size class category.  To view one plot at a time select from drop down below, or download compiled PDF [here](https://github.com/rswaty/ABRPweb/raw/master/PineSeedlingsCats.pdf). 

```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
sdSeedlings <- highlight_key(seedlings)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
pineSeedlings <-  
ggplot(sdSeedlings, aes(MONYEAR, STEMS)) +
  geom_line(aes(group = 1), size = 0.5, color = '#54524d') +
  geom_point() +
  labs(
    title = "Pine seedlings per plot (coded)",
    subtitle = "Including size class",
    caption = "Data from TNC's Florida Chapter",
    x = "Year",
    y = "Stem count code" ) 

bscols(widths = c(5, 12),
       filter_select("BP", 
                     "Plot:", 
                     sdSeedlings, 
                     ~ BP,
                     multiple = FALSE),
       ggplotly(pineSeedlings)
)

```


# Raw seedling counts, 2012-2020

```{r meanSeedlings2012-2020, echo=FALSE, message=FALSE, warning=FALSE, fig.align='left', fig.width=10, fig.height=7}

seedlings2012 <- seedlings %>%
  filter(MONYEAR > 2011)

seedlings2012SE <-  summarySE(seedlings2012, measurevar = 'STEMSraw', groupvars = "MONYEAR")


seedlingsExplore2012 <-
  seedlings2012SE %>%
  ggplot(aes(x = MONYEAR, y = STEMSraw)) +
  geom_errorbar(aes(ymin=STEMSraw-se, ymax=STEMSraw+se), width = 0.2, color = '#9c9991', size = 0.8) +
  geom_line(size = 1.0, color = '#54524d') +
  geom_point() +
  geom_smooth(method=lm) +
  labs(x = "Year",
       y = " Raw Stem count",
       title = "Mean seedlings per year, 2012-2020",
       subtitle = "Trend line fitted with linear model, level of confidence = 0.95",
       caption = "Data from Florida Chapter")  +

  #Adjust the axes, remove legend
  theme(legend.position = "none",
        plot.title = element_text(face="bold"),
        axis.title.x = element_text(face="bold"),
        axis.title.y = element_text(face="bold"))

seedlingsExplore2012
```



Number of stems per size class category.  To view one plt at a time select from drop down below, or download compiled PDF [here](https://github.com/rswaty/ABRPweb/raw/master/PineSeedlingsRAW.pdf). 


```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}
#make shared data for crosstalk
seedlings2012sd <- highlight_key(seedlings2012)

```


```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}
pineSeedlings2012 <-  
ggplot(seedlings2012sd, aes(MONYEAR, STEMSraw)) +
  geom_line(aes(group = 1), size = 0.5, color = '#54524d') +
  geom_point() +
  theme_bw() +
  labs(
    title = "Pine seedlings per plot, 2012-2020",
    subtitle = "Including size class",
    caption = "Data from TNC's Florida Chapter",
    x = "Year",
    y = "Raw stem count" ) 

bscols(widths = c(5, 12),
       filter_select("BP", 
                     "Plot:", 
                     seedlings2012sd, 
                     ~ BP,
                     multiple = FALSE),
       ggplotly(pineSeedlings2012)
)

```
